rapr: Representative and Adequate Prioritisations in R

### 2016-06-14 code/rmarkdown/figures.Rmd
* version 1 + debugging parameters work

---
fontsize: 11pt
documentclass: article
bibliography: Endnote_lib.bib
csl: reference-style.csl
output:
  rmarkdown::pdf_document:
    fig_caption: yes
    keep_tex: yes
    includes:
      in_header: [preamble-latex.tex, preamble-latex2.tex]
---

@@

@@

>>>>

---
fontsize: 11pt
documentclass: article
bibliography: references.bib
csl: reference-style.csl
output:
  rmarkdown::pdf_document:
    fig_caption: yes
    keep_tex: yes
    includes:
      in_header: [preamble-latex.tex, preamble-latex2.tex]
---

@@

# prelimary processing
sim.pus.FPLY <- fortify(sim.pus)
aus.FPLY <- fortify(aus.PLY)
cs1.pus.FPLY <- fortify(cs1.pus)
cs2.grid.FPLY <- fortify(cs2.grid.PLY)
cs2.grid.sub.FPLY <- fortify(cs2.grid.sub.PLY)

# store countries
data(countriesHigh)
countries.FPLY <- countriesHigh[
	countriesHigh$ADMIN %in% c(
		'Italy', 'Switzerland', 'France', 'Austria',
		'Germany', 'Slovenia', 'Croatia', 'Hungary',
		'Monaco', 'Germany', 'Slovakia', 'Czech Republic'
	)
,] %>% spFortify

@@

## Figures

```{r, echo=FALSE, message=FALSE, fig.height=2, fig.width=2, fig.cap="Example of an attribute space. This environmental attribute space has dimensions relating to annual temperature ($^{\\circ}$C) and rainfall (ml) values. Letters denote the environmental conditions associated with the geographic locations where four hypothetical populations are found. Points represent demand points. In this space, populations closer to each other are considered more similar to each other."}
## generate data
# population data
populations <- data.frame(
	population=LETTERS[1:4],
	temperature=c(22,29,21.6,34),
	rainfall=c(6,12,5.5,6)
)
# demand point data
make.dp <- function(x, n, pad.percent=0.2) {
	padding<-diff(range(x))*pad.percent
	return(seq(min(x)-padding, max(x)+padding, length.out=n))
}
demand.points <- expand.grid(
	temperature=make.dp(populations$temperature, n=4, pad.percent=0.2),
	rainfall=make.dp(populations$rainfall, n=4, pad.percent=0.2)
)

## plot data
ggplot(aes(x=temperature, y=rainfall), data=populations) +
	geom_point(data=demand.points, fill='gray70') +
	geom_text(aes(label=population), size=6) +
	theme_classic() +
	xlab(expression('Temperature ('*degree*'C)')) +
	ylab('Rainfall (mm)') +
	theme(axis.line.x=element_line(), axis.line.y=element_line())
```

```{r, echo=FALSE, messages=FALSE, results='hide', fig.height=1.5, fig.width=4.5, fig.cap='Simulation study. Squares denote planning units. Each panel shows the distribution for a different simulated species. The fill of each planning unit indicates the probability that a given species inhabits it. Panel (a) shows the uniformly distributed species, panel (b) shows the normally distributed species, and panel (c) shows the bimodally distributed species.'}
# prepare data
sim.pus.occ.FPLY <- ldply(
	seq_len(nrow(sim.species)),
	function(i) {
		curr.DF <- sim.pus.FPLY
		curr.DF$species <- sim.species$name[i]
		curr.DF$Probability <- sim.dps[[i]]@weights[as.numeric(curr.DF$id)]
		return(curr.DF)
	}
)
sim.pus.occ.FPLY$species <- gsub('\n', ' ', as.character(sim.pus.occ.FPLY$species))
sim.pus.occ.FPLY$species <- factor(as.character(sim.pus.occ.FPLY$species), levels=gsub('\n', ' ', sim.species$name)) 
# make plot
ggplot() +
	geom_polygon(data=sim.pus.occ.FPLY, aes(x=long, y=lat, group=group, fill=Probability), color='black') +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 5, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(),
		legend.position=c(1.15, 0.6)) +
	facet_wrap(~ species, ncol=3)
```

```{r, echo=FALSE, fig.height=4.5, fig.width=4.0, fig.cap='Species used in the first case-study. Squares denote planning units. Each panel shows the distribution of a given species. For a given species, planning units inhabited by the species are shown in bright blue and those uninhabited are shown in dark blue.'}
# prepare data
cs1.pus.occ.FPLY <- ldply(
	seq_along(cs1.params.LST[[MODE]]$common.names),
	function(i) {
		curr.DF <- cs1.pus.FPLY
		curr.DF$species <- cs1.params.LST[[MODE]]$common.names[i]
		curr.DF$Occupancy <- 'absent'
		curr.DF$Occupancy[which(curr.DF$id %in% filter(cs1.ru@data@pu.species.probabilities, species==i)$pu)] <- 'present'
		return(curr.DF)
	}
)
cs1.pus.occ.FPLY$species <- factor(as.character(cs1.pus.occ.FPLY$species), levels=cs1.params.LST[[MODE]]$common.names)
# make plots
ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_polygon(data=cs1.pus.occ.FPLY, aes(x=long, y=lat, group=group, fill=Occupancy), color='black') +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='transparent', fill='transparent'),
		legend.position=c(1.045, 1.035), legend.justification=c(1,1), legend.key.size=unit(3, 'mm')
	) +
	scale_fill_manual(name='Occupancy', values=c('absent'='#132B43', 'present'='#56B1F7')) +
	coord_cartesian(xlim=cs1.pus@bbox[1,], ylim=cs1.pus@bbox[2,]) +
	facet_wrap(~ species, ncol=2)
```

```{r, echo=FALSE, fig.height=2.5, fig.width=3, fig.cap='Distribution of environmental variation across Queensland, Australia. Squares denote planning units. The panels show the first and second main gradients of climatic variation.'}
# prepare data
cs1.pca.FPTS <- ldply(
	seq_len(cs1.params.LST[[MODE]]$n.pc.layers),
	function(i) {
		curr.DF <- cs1.bioclim.RAST[[i]] %>% 
			aggregate(10) %>% 
			rasterToPoints() %>% 
			as.data.frame()
		names(curr.DF)[3] <- 'Score'
		curr.DF$pc <- paste0('Principal component ',i)
		return(curr.DF)
	}
)
# make plots
p1 <- ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_raster(data=filter(cs1.pca.FPTS, pc==unique(pc)[1]), aes(x=x, y=y, fill=Score)) +
	geom_polygon(data=cs1.pus.FPLY, aes(x=long, y=lat, group=group), fill=NA, color='black') +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='transparent', fill='transparent'),
		legend.position=c(1.1, 1.07), legend.justification=c(1,1), legend.key.size=unit(3, 'mm')
	) +
	coord_cartesian(xlim=cs1.pus@bbox[1,], ylim=cs1.pus@bbox[2,]) +
	facet_wrap(~ pc)
p2 <- ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_raster(data=filter(cs1.pca.FPTS, pc==unique(pc)[2]), aes(x=x, y=y, fill=Score)) +
	geom_polygon(data=cs1.pus.FPLY, aes(x=long, y=lat, group=group), fill=NA, color='black') +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='transparent', fill='transparent'),
		legend.position=c(1.1, 1.07), legend.justification=c(1,1), legend.key.size=unit(3, 'mm')
		) +
	coord_cartesian(xlim=cs1.pus@bbox[1,], ylim=cs1.pus@bbox[2,]) +
	facet_wrap(~ pc)
# render plots
grid.arrange(p1, p2, ncol=2)
```

```{r, echo=FALSE, fig.height=4.5, fig.width=4.5, fig.cap=paste0('Study area for the second case-study. Squares denote planning units. Panel (a) shows the planning units occupied by ',cs2.params.LST[[MODE]]$common.name,'. Panels (b--c) show the spatial distribution of the ordinated values that describe patterns of genetic variation associated this species.')}
# prepare full grid data
cs2.spp.grid.FPLY <- cs2.grid.FPLY
cs2.spp.grid.FPLY$Title <- 'Occupancy'
cs2.spp.grid.FPLY$Occupancy <- 'absent'
cs2.spp.grid.FPLY$Occupancy[which(cs2.grid.PLY@data[[cs2.params.LST[[MODE]]$species.name]][as.numeric(cs2.spp.grid.FPLY$id)]==1)] <- 'present'

# prepare subset grid data
cs2.spp.grid.sub.FPLY <- cs2.grid.sub.FPLY
cs2.spp.grid.sub.FPLY$nmds1 <- NA
cs2.spp.grid.sub.FPLY$nmds2 <- NA
cs2.nmds1 <- cs2.grid.sub.DF[[paste0(cs2.params.LST[[MODE]]$species.name,'_genetic_d1')]]
cs2.nmds2 <- cs2.grid.sub.DF[[paste0(cs2.params.LST[[MODE]]$species.name,'_genetic_d2')]]

curr.pos <- match(as.numeric(cs2.spp.grid.sub.FPLY$id), cs2.grid.sub.DF$id)
cs2.spp.grid.sub.FPLY$nmds1 <- cs2.nmds1[curr.pos]
cs2.spp.grid.sub.FPLY$nmds2 <- cs2.nmds2[curr.pos]

cs2.spp.grid.sub.FPLY$Cost <- costs.MTX[match(cs2.grid.sub.PLY$id[as.numeric(cs2.spp.grid.sub.FPLY$id)], costs.MTX[,1]),2]

cs2.spp.grid.sub.FPLY$Title1 <- 'Opportunity cost'
cs2.spp.grid.sub.FPLY$Title2 <- 'Genetic NMDS 1'
cs2.spp.grid.sub.FPLY$Title3 <- 'Genetic NMDS 2'

# plot species data
p1 <- ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_polygon(data=cs2.spp.grid.FPLY, aes(x=long, y=lat, group=group, fill=Occupancy), alpha=0.8, color='grey10') +
	theme_classic() +
	theme(
		axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.position='none'
	) +
	scale_fill_manual(name='Occupancy', values=c('absent'='#132B43', 'present'='#56B1F7')) +
	coord_cartesian(xlim=buffered.range(cs2.grid.FPLY$long, 0), ylim=buffered.range(cs2.grid.FPLY$lat, 0)) +
	facet_wrap(~ Title)
# plot cost data
p2 <- ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_polygon(data=cs2.spp.grid.sub.FPLY, aes(x=long, y=lat, group=group, fill=Cost), alpha=0.8, color='grey10') +
	theme_classic() +
	theme(
		axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='black', fill='white'),
		legend.position=c(1, 0), legend.justification=c(1,0), legend.key.size=unit(3, 'mm'),
		legend.title=element_blank()
	) +
	coord_cartesian(xlim=buffered.range(cs2.grid.sub.FPLY$long, 0), ylim=buffered.range(cs2.grid.sub.FPLY$lat, 0)) +
	scale_fill_continuous(NULL) +
	facet_wrap(~ Title1)
# plot nmds axis 1
p3 <- ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),fill='grey85', color='grey70') +
	geom_polygon(data=cs2.spp.grid.sub.FPLY, aes(x=long, y=lat, group=group, fill=nmds1), alpha=0.8, color='grey10') +
	theme_classic() +
	theme(
		axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='black', fill='white'),
		legend.position=c(1, 0), legend.justification=c(1,0), legend.key.size=unit(3, 'mm')
	) + 
	coord_cartesian(xlim=buffered.range(cs2.grid.sub.FPLY$long, 0), ylim=buffered.range(cs2.grid.sub.FPLY$lat, 0)) +
	scale_fill_gradient2(name=element_blank(), low='darkblue', mid='white', high='darkred') +
	facet_wrap(~ Title2)
# plot nmds axis 2
p4 <- ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),fill='grey85', color='grey70') +
	geom_polygon(data=cs2.spp.grid.sub.FPLY, aes(x=long, y=lat, group=group, fill=nmds2), alpha=0.8, color='grey10') +
	theme_classic() +
	theme(
		axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='black', fill='white'),
		legend.position=c(1, 0), legend.justification=c(1,0),   legend.key.size=unit(3, 'mm')
	) + 
	coord_cartesian(xlim=buffered.range(cs2.grid.sub.FPLY$long, 0), ylim=buffered.range(cs2.grid.sub.FPLY$lat, 0)) +
	scale_fill_gradient2(name=element_blank(), low='darkblue', mid='white', high='darkred') +
	facet_wrap(~ Title3)
# render plots
grid.arrange(p1, p2, p3, p4, ncol=2)
```

```{r, echo=FALSE, fig.height=3.5, fig.width=5, fig.cap=paste0('Simulation study prioritisations. Squares denote planning units. The fill of each planning unit denotes the probability that it is occupied by a given species. The color the border of each planning unit indicates if it was selected for prioritisation. Each panel shows the prioritisation resulting from a given species and parameters. Each row of panels corresponds to a different species. The top row of panels (a,d,g,j ) shows prioritisations generated for the uniformly distributed species, middle row of panels (b,e,h,k) for the normally distributed species, and the bottom row of panels (c,f,i,l) for the bimodally distributed species. Each column of panels correpsonds to a different set of parameters used to generate the prioritisation. The left column of panels (a--c) shows prioritizations generated using only ',(sim.params.LST[[MODE]]$amount.target*100),' % amount targets, the middle-left column of panels (d--f) for prioritisations generated using ',(sim.params.LST[[MODE]]$amount.target*100),' % amount and ',(sim.params.LST[[MODE]]$space.target*100),' % space targets, the middle-right column of panels (g--i) for prioritisations generated using ',(sim.params.LST[[MODE]]$amount.target*100),' % amount based targets and a boundary length modifier (BLM) of ',sim.params.LST[[MODE]]$blm,', and the right column of panels (j--l) for prioritisations generated using ',(sim.params.LST[[MODE]]$amount.target*100),' % amount and ',(sim.params.LST[[MODE]]$space.target*100),' % space targets and also a boundary length modifier of ',(sim.params.LST[[MODE]]$blm),'.')}
# prepare data
sim.pus.sel.FPLY <- ldply(
	seq_len(nrow(sim.spp.DF)),
	function(i) {
		curr.DF <- sim.pus.FPLY %>% mutate(species=sim.spp.DF$species[i], prioritisation=sim.spp.DF$prioritisation[i])
		curr.selection <- selections(sim.prioritisations[[sim.spp.DF$species[i]]][[sim.spp.DF$prioritisation[i]]])[as.numeric(curr.DF$id)]
		curr.DF$Selection <-  c('discarded','selected')[curr.selection+1]
		return(curr.DF)
	}
)
sim.pus.sel.FPLY$prioritisation <- factor(as.character(sim.pus.sel.FPLY$prioritisation),
	levels=c('Amount\ntargets', 'Amount &\nspace targets', 'Amount target\nand BLM', 'Amount & space\ntargets and BLM'))
# prepare plotting data
sim.letter.DF2 <- mutate(sim.spp.DF, letter=paste0('(', letters[seq_along(species)],')'))
sim.letter.DF2$long <- gCentroid(sim.pus[1,])@coords[1]
sim.letter.DF2$lat <- gCentroid(sim.pus[1,])@coords[2]
# make plot
ggplot() +
	geom_polygon(data=sim.pus.sel.FPLY, aes(x=long, y=lat, group=group, fill=Selection), color='black') +
	geom_text(data=sim.letter.DF2, aes(label=letter, x=long, y=lat), color='black', size=3) +
	theme_classic() +
	theme(
		axis.ticks=element_blank(), axis.ticks.x=element_blank(), axis.ticks.y=element_blank(),
		axis.text=element_blank(), axis.text.x=element_blank(), axis.text.y=element_blank(),
		axis.line=element_blank(), axis.line.x=element_blank(), axis.line.y=element_blank(),
		plot.background=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		panel.background=element_blank(), panel.border=element_blank(), legend.position='none',
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank()) +
	scale_fill_manual(name='Solution', values=c('discarded'='#f7fcfd', 'selected'='#00441b')) +
	facet_grid(species ~ prioritisation)
```

```{r, echo=FALSE, fig.height=2.5, fig.width=4.5, fig.cap=paste0('Prioritisations for the niche-based case-study in Queensland, Australia. Squares represent planning units. Dark green planning units for selected for protection and pale green units were discarded. Panel (a) shows the planning units selected when using ',cs1.params.LST[[MODE]]$amount.target*100,' % amount targets. Panel (b) shows the planning units selected selected when using ',cs1.params.LST[[MODE]]$amount.target*100,' % amount targets and ',cs1.params.LST[[MODE]]$space.target*100,' % niche targets')}
# prepare data
cs1.pus.sel.FPLY <- ldply(
	names(cs1.prioritisations),
	function(x) {
		curr.DF <- cs1.pus.FPLY
		curr.DF$Prioritisation <- x
		curr.DF$Solution <- 'discarded'
		curr.DF$Solution[curr.DF$id %in% which(as.logical(selections(cs1.prioritisations[[x]])))] <- 'selected'
		return(curr.DF)
	}
)
cs1.pus.sel.FPLY$Prioritisation <- factor(as.character(cs1.pus.sel.FPLY$Prioritisation), levels=names(cs1.prioritisations))
# make plots
ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_polygon(data=cs1.pus.sel.FPLY, aes(x=long, y=lat, group=group, fill=Solution), color='black') +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='transparent', fill='transparent'),
		legend.position=c(1.03, 1.03), legend.justification=c(1,1), legend.key.size=unit(3, 'mm')
	) +
	scale_fill_manual(name='Solution', values=c('discarded'='#f7fcfd', 'selected'='#00441b')) +
	coord_cartesian(xlim=cs1.pus@bbox[1,], ylim=cs1.pus@bbox[2,]) +
	facet_wrap(~ Prioritisation, ncol=2)
```

```{r, echo=FALSE, fig.height=5, fig.width=5, fig.cap=paste0('Prioritisations for the genetic case-study in the European Alps. Panel (a) shows the planning units selected when using ',cs2.params.LST[[MODE]]$amount.target*100,' % amount targets. Panel (b) shows the planning units selected selected when using ',cs2.params.LST[[MODE]]$amount.target*100,' % amount targets and ',cs2.params.LST[[MODE]]$genetic.target*100,' % genetic targets. The conventions for panels (a--b) are detailed in the caption for Figure 7. Panels (c--d) show the solutions in the genetic space. In these panels, each point is an average of the ordinations for individuals in each planning unit. Each point represents the typical genetic characeristics of individuals sampled in a given planning unit (based on an NMDS of the binary loci data). Planning units associated with points that are closer togeather contain individuals with more similar genetic characteristics than planning units that are further apart. Dark green planning units were selected for protection, and pale green planning units were discarded.')}
# prepare spatial data
cs2.sel.grid.sub.FPLY <- cs2.grid.sub.FPLY
cs2.sel.grid.sub.FPLY$Title1 <-'Amount target'
cs2.sel.grid.sub.FPLY$Title2 <- 'Amount & genetic target'

cs2.sel.grid.sub.FPLY$Amount.selection <- 'discarded'
cs2.sel.grid.sub.FPLY$Amount.selection[cs2.sel.grid.sub.FPLY$id %in% which(as.logical(selections(cs2.prioritisations[[1]])))] <- 'selected'

cs2.sel.grid.sub.FPLY$Amount.genetic.selection <- 'discarded'
cs2.sel.grid.sub.FPLY$Amount.genetic.selection[cs2.sel.grid.sub.FPLY$id %in% which(as.logical(selections(cs2.prioritisations[[2]])))] <- 'selected'

# prepare genetic space plots
cs2.sel.space.DF <- data.frame(cs2.genetic.AS@spaces[[1]]@planning.unit.points@coords)
names(cs2.sel.space.DF) <- c('d1', 'd2')
cs2.sel.space.DF$id <- cs2.genetic.AS@spaces[[1]]@planning.unit.points@ids

cs2.sel.space.DF$Amount.selection <- 'discarded'
cs2.sel.space.DF$Amount.selection[cs2.sel.space.DF$id %in% which(as.logical(selections(cs2.prioritisations[[1]])))] <- 'selected'

cs2.sel.space.DF$Amount.genetic.selection <- 'discarded'
cs2.sel.space.DF$Amount.genetic.selection[cs2.sel.space.DF$id %in% which(as.logical(selections(cs2.prioritisations[[2]])))] <- 'selected'

# make plots
p1 <- ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_polygon(data=cs2.sel.grid.sub.FPLY, aes(x=long, y=lat, group=group, fill=Amount.selection), color='black') +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='black', fill='white'),
		axis.title=element_blank(), legend.position='none'
	) +
	scale_fill_manual(name='Solution', values=c('discarded'='#f7fcfd', 'selected'='#00441b', 'uninhabited'='grey65')) +
	coord_cartesian(xlim=cs2.grid.sub.PLY@bbox[1,], ylim=cs2.grid.sub.PLY@bbox[2,]) +
	facet_wrap(~ Title1)
p2 <- ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_polygon(data=cs2.sel.grid.sub.FPLY, aes(x=long, y=lat, group=group, fill=Amount.genetic.selection), color='black') +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='black', fill='white'),
		legend.position=c(1, 0), legend.justification=c(1,0), legend.key.size=unit(3, 'mm')
	) +
	scale_fill_manual(name='Solution', values=c('discarded'='#f7fcfd', 'selected'='#00441b', 'uninhabited'='grey65')) +
	coord_cartesian(xlim=cs2.grid.sub.PLY@bbox[1,], ylim=cs2.grid.sub.PLY@bbox[2,]) +
	facet_wrap(~ Title2)
p3 <- ggplot() +
	geom_point(data=cs2.sel.space.DF, aes(x=d1, y=d2, fill=Amount.selection), pch=21, size=3, color='black') +
	theme_classic() + xlab('Genetic NMDS Axis 1') + ylab('Genetic NMDS Axis 2') +
	theme(legend.position='none', axis.line.x=element_line(), axis.line.y=element_line()) +
	scale_fill_manual(name='Solution', values=c('discarded'='transparent', 'selected'='#00441b'))
p4 <- ggplot() +
	geom_point(data=cs2.sel.space.DF, aes(x=d1, y=d2, fill=Amount.genetic.selection), pch=21, size=3, color='black') +
	theme_classic() + xlab('Genetic NMDS Axis 1') + ylab('Genetic NMDS Axis 2') +
	theme(legend.position='none', axis.line.x=element_line(), axis.line.y=element_line()) +
	scale_fill_manual(name='Solution', values=c('discarded'='transparent', 'selected'='#00441b'))
# render plots
grid.arrange(p1,p2,p3,p4,ncol=2)

### 2016-06-14 code/rmarkdown/supporting-information.Rmd
* version 1 + debugging parameters work

---
fontsize: 11pt
documentclass: article
bibliography: Endnote_lib.bib
csl: reference-style.csl
output:
  rmarkdown::pdf_document:
    fig_caption: yes
    keep_tex: yes
    includes:
      in_header: [preamble-latex.tex, preamble-latex3.tex]
---
## Supporting Information
All data and code is stored in an online repository (\url{www.github.com/paleo13/rapr-manuscript}) to replicate analyses in this study. See the \textit{README} file for instructions.

>>>>

---
fontsize: 11pt
documentclass: article
bibliography: references.bib
csl: reference-style.csl
output:
  rmarkdown::pdf_document:
    fig_caption: yes
    keep_tex: yes
    includes:
      in_header: [preamble-latex.tex, preamble-latex3.tex]
---
## Supporting Information
All data and code is stored in an online repository (\url{www.github.com/paleo13/rapr-manuscript}) to replicate analyses in this study. See the \textit{README} file for instructions.
